\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-03-17 chapters/3_algorithm.tex
Update list of update rules and associated algs.

\section{Unified Graph Agglomerative Clustering}
In this section we introduce a unified agglomerative clustering algorithm that represents a simple generalized formalization of many agglomerative graph clustering algorithms. It can be used to describe both unsigned clustering algorithms ingesting positive cluster similarities and signed clustering algorithms using attractive and repulsive cues.\\
First, we define the graph notation and the concept of cannot-link constraints. Then, we introduce the generalized algorithm and show \UPDATE{how it can be used to introduce several new agglomerative clustering algorithms for graphs with signed weights.}

@@

We consider a graph $\mathcal{G}(V,E,W)$ with associated signed edge weights, where each node initially represents one cluster.
The proposed graph partitioning algorithm is a general form of agglomerative clustering that outputs a final graph clustering $\Pi$ by progressively merging pairs of neighboring clusters. The algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \ref{fig:general_idea}b and \ref{fig:general_idea}c).

@@

During the agglomerative process, the interaction between neighboring clusters is defined by the linkage criterion defined in Equation \ref{eq:linkage_criterion_def} and has to be properly recomputed. 
One possible efficient way of doing this is to use an edge contraction algorithm like the one presented in Algorithm \ref{main_alg}, which proceeds as follows.

@@

 In the special case of an unsigned graph %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 presenting strictly positive similarities between nodes, the algorithm then returns only one single cluster as an output (see Fig. \ref{fig:intro_figure}a), \UPDATE{together with a merging tree representing the merging order and defining an hierarchy of clusters} \TODO{use def of merging process of contracted graph to define merging tree}.

@@

\subsection{Update rules and associated algorithms}
\begin{itemize}
\item In this section we will list \UPDATE{ALL} (...) algorithms that can be described using the generalized algorithm we presented and define some new ones
\item In Table 1 we collected the update rules we tested and compared in this article (correspond to the simplest and cheapest ones to compute). Later we will mention more of them
\item First unsigned graphs: the merging tree defined by the algorithm (\textbf{define merge tree somewhere..?}) is equivalent to the hierarchical dendrogram (but careful with the sum...) that we have in HC
\item Then mention CLC and who started using them recently for this type of problem: fixed, then greedyFixation introduced exactly this algorithm as a greedy approx of MC, together with Greedy Additive Edge Contraction
\item MWS: proposes an efficient implementation of this update rule (briefly mention the idea). In the Supplementary material we show that the algorithm they present can be seen as a special case of Unified Graph Agglomerative Clustering with absolute maximum update rule and that adding or not CLC does not change anything
\item Then new versions of avg/complete and single linkage clustering 
\item In this article we analyze only the simplest (and cheapest) types of update rules, but... Easily generalizable for: learned linkage criteria \cite{nunez2013machine}, something depending on node size \cite{felzenszwalb2004efficient}, quantiles, weighted average (WPGMA) and weighted sum (and related work by Paul), size rule by Thorsten
\item comment about the fact that sum is not really an ultra-metric-distance
\end{itemize}

>>>>

\section{Unified Graph Agglomerative Clustering}
In this section we introduce the Unified Graph Agglomerative Clustering Algorithm (UGACA) that represents a simple generalized formalization of many agglomerative graph clustering algorithms. \UPDATE{It can be used to describe both unsigned clustering algorithms ingesting positive cluster similarities and signed clustering algorithms using attractive and repulsive cues.}\\
First, we define the graph notation and the concept of cannot-link constraints. Then, we introduce the generalized algorithm and show \UPDATE{how it can be used to introduce several new agglomerative clustering algorithms for graphs with signed weights.}

@@

We consider a graph $\mathcal{G}(V,E,W)$ with associated signed edge weights, where each node initially represents one cluster.
The proposed graph partitioning algorithm is a general form of agglomerative clustering that outputs a final graph clustering $\Pi$ by progressively merging pairs of neighboring clusters. Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \ref{fig:general_idea}b and \ref{fig:general_idea}c).

@@

During the agglomerative process, the interaction between neighboring clusters is defined by the linkage criterion defined in Equation \ref{eq:linkage_criterion_def} and has to be properly updated and recomputed. 
An efficient way of implementing these updates can be achieved by using the presented edge contraction Algorithm \ref{main_alg}, which proceeds as follows.

@@

 In the special case of an unsigned graph %$\mathcal{G}(V,E,W:E\rightarrow \mathbb{R}^+)$ 
 presenting strictly positive similarities between nodes, the algorithm then returns only one single cluster as an output (see Fig. \ref{fig:intro_figure}a), \UPDATE{together with a merging tree representing the merging order and defining an hierarchy of clusters} \TODO{use def of merging process of contracted graph to define merging tree?}.

@@

\subsection{Update rules and associated algorithms}
\begin{itemize}
\item In this section we will list some of the algorithms that can be described using the generalized algorithm we presented and define some new ones
\item In Table 1 we collected the update rules we tested and compared in this article (correspond to the simplest and cheapest ones to compute). Later we will mention more of them that were proposed in the literature.
\item In the special case of unsigned graphs (Table \ref{tab:linkage-criteria} column 1), the UGAC algorithm becomes simply a version of hierarchical clustering with different linkage criteria depending on the chosen update rule. It outputs one single cluster and it also defines an hierarchy of clusters during the merging process that can be associated to \UPDATE{a merging tree/  the hierarchical clustering dendrogram}... \TODO{Problem: sum does not trivially define an ultra-metric-distance...}  
\item In the literature there have been already several methods using cannot-link constraints for agglomerative clustering algorithms \TODO{repetition from related work}: for example, \cite{malmberg2011generalized} used initially fixed mutual exclusion relationships, whereas \cite{levinkov2017comparative} introduced them dynamically in an edge contraction algorithm for signed graphs, named Greedy Fixation (Table \ref{tab:linkage-criteria} row 1, \emph{sum}). At the same time, they also proposed a version of it without cannot link constraints (Greedy Additive Edge Contraction) and they compared both with other greedy and local-search algorithms for solving the multicut/correlation clustering problem.
\item Dynamically introduced cannot-link constraints were also proposed by \cite{wolf2018mutex}, that... \TODO{brief MWS description as efficient implementation of this update rule}. In the Supplementary material we show that the algorithm they present can be seen as a special case of UGACA with absolute maximum update rule (Table \ref{tab:linkage-criteria} row 2 - \emph{absolute maximum}) and that adding or not cannot-link constraints does not change the final clustering.
\item On the other hand, the signed graph versions of UGACA with update rules \emph{arithmetic mean}, \emph{max} and \emph{min} (rows 3 to 5 in Table \ref{tab:linkage-criteria}) are new algorithms that were never mentioned in the literature, \UPDATE{especially those with cannot-link constraints}.
\item In this article, we test and run a comparison of the five types of update rule listed in Table \ref{tab:linkage-criteria} (i.e. \emph{sum}, \emph{absolute mac}, \emph{arithmetic mean}, \emph{max} and \emph{min}), since \UPDATE{they they are the most commonly used and the cheapest to compute}. Nevertheless, UGACA can be easily generalized to include even more complex rules. For instance, \cite{nunez2013machine} proposes a learned version of update rule where a neural network updates the edge weights depending on edge and node features; another really common choice is to introduce a weight regularization depending on the size of the linked nodes (\cite{felzenszwalb2004efficient} and \cite{kardoostsolving} (unpublished...??), Thorsten..); 
\cite{funke2018large} on the other hand accumulate statistics for each \UPDATE{boundary between clusters} by keeping a discrete histograms of the edge weights and then computes quantiles from it.
\end{itemize}
